From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-08-08 WOLFHPC15/article/introduction.tex
fix accents et taille references helene 08_08

Many solutions to automatically optimize and parallelize partial differential equations (PDEs) codes have been proposed in the literature, either as specific frameworks~\cite{CPE:CPE3494} or as DSLs~\cite{spaaTangCKLL11,citeulike12258902,Giles2011,DeVito2011LDS}. Most of the time, DSLs focus on the parallelization and the optimization of a single numerical computation, also called a stencil kernel.
However, a real case numerical simulation (such as fluid dynamics, magnetohydrodynamics, molecular synamics etc.) is most of the time not composed of a single stencil kernel, but of a set of stencil kernels and a set of additional local auxiliary computations. The DSL proposed in this paper, called MSL, is a DSL to generate a parallel component-based structure of an overall numerical simulation, that we call a \emph{multi-stencil program}. As it will be detailed in the related work, this is complementary to the optimization and parallelization of a single stencil kernel.

>>>>

Many solutions to automatically optimize and parallelize partial differential equations (PDEs) codes have been proposed in the literature, either as specific frameworks~\cite{CPE:CPE3494,Trilinos-Overview,petsc-efficient} or as DSLs~\cite{spaaTangCKLL11,citeulike12258902,Giles2011,DeVito2011LDS}. Most of the time, DSLs focus on the parallelization and the optimization of a single numerical computation, also called a stencil kernel.
However, a real case numerical simulation (such as fluid dynamics, magnetohydrodynamics, molecular synamics etc.) is most of the time not composed of a single stencil kernel, but of a set of stencil kernels and a set of additional local auxiliary computations. The DSL proposed in this paper, called MSL, is a DSL to generate a parallel component-based structure of an overall numerical simulation, that we call a \emph{multi-stencil program}. As it will be detailed in the related work, this is complementary to the optimization and parallelization of a single stencil kernel.
